---
title: "Indiana Early Childhood"
output:
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      bootswatch: sandstone
      base_font: 
        google: Castoro
      heading_font:
        google: Lato
      code_font:
        google: 
          # arguments to sass::font_google() 
          family: Roboto Mono
          local: false
      font_scale: 1
    css: my-css-rules.css
    mathjax: NULL
    orientation: columns
    vertical_layout: fill
    source_code: embed
    includes:
      after_body: ./includes/footer.html
  bibliography: ./refs.bib

---

```{r setup, include=FALSE}
library(flexdashboard)
library(magrittr)
library(dplyr)
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()
```

```{r load-data}
input <- "./data/tidy/2021-06-25-maternal-infant-health.csv"
df <- data.table::fread(input = input)
# prepare data
rownames(df) <- df$location
df.1 <- df %>% select(-location)
```

# Maternal Health {data-icon="fas fa-child"}

## Column {data-width=600}{.tabset}

### Heatmap

```{r heatmap-maternal-health}
load("./data/tidy/hm_mh.Rdata")
hm_mh
```

### Correlogram

```{r correlogram-maternal-health}
load("./data/tidy/cg_mh.Rdata")
cg_mh
```

## Column {data-width=400}

### Top 20 Indiana Counties by Live Births

```{r table-maternal-health}
library(DT)
row.names(df) <- NULL
DT::datatable(df, 
              extensions = 'FixedColumns',
              class = 'compact stripe',
              rownames = F,
  options = list(
    pageLength = 20,
    dom = 't',
    scrollX = TRUE,
    fixedColumns = list(leftColumns = 1)
  )) %>% 
  formatPercentage(columns = c(2:13), digits = 1)
```
### Tip {data-height=150}

The "Heatmap" shows the variation among Indiana's top counties by live births. The comparisons are by column. Look for the bright yellows and dark blues within a single column.  Also, look to see how the algorithm grouped the counties and variables with the dendrogram in the margins.

The "Correlogram" is a correlation matrix showing the relationship between the numeric variables.



# Early Childhood {data-icon="fas fa-school"}

## Column {data-width=600}{.tabset}

### Heatmap

```{r heatmap-early-childhood}
load("./data/tidy/hm_ec.Rdata")
hm_ec
```

### Correlogram

hello

```{r correlogram-early-childhood}
load("./data/tidy/cg_ec.Rdata")
cg_ec
```


## Column {data-width=400}

### Top 20 Indiana Counties by Children Age 0 to 4

```{r table-early-childhood}
file <- "./data/tidy/2021-06-28-in-early-childhood.csv"
ec <- readr::read_csv(file = file)
library(DT)
row.names(ec) <- NULL
DT::datatable(ec, 
              extensions = 'FixedColumns',
              class = 'compact stripe',
              rownames = F,
  options = list(
    pageLength = 20,
    dom = 't',
    scrollX = TRUE,
    fixedColumns = list(leftColumns = 2))) %>% 
  formatRound(columns = 3:20, digits = 3)
```

### Tip {data-height=150}

The "Heatmap" shows the variation among Indiana's top counties by live births. The comparisons are by column. Look for the bright yellows and dark blues within a single column.  Also, look to see how the algorithm grouped the counties and variables with the dendrogram in the margins.

The "Correlogram" is a correlation matrix showing the relationship between the numeric variables.

# Public Health Funding

## Column {data-width=600}

### Chart

## Column {data-width=400}

### Key Points

-  $3.6 trillion annually on health, less than 3 percent of that spending is directed toward public health and prevention.

- Public health spending as a proportion of total health spending has been decreasing since 2000 and falling in inflation-adjusted terms since the Great Recession.

- U.S. Centers for Disease Control and Prevention (CDC) is the primary driver of federal public health funding through its grant programs to the states and large cities.

- Most states (39) and the District of Columbia increased or maintained funding for public health budgets in FY 2019, but 11 states decreased such funding.

[Trust for America's Health](https://www.tfah.org/report-details/publichealthfunding2020/)


### Citation {data-height=150}

Lasner, M. G. (2012). High Life: Condo Living in the Suburban Century. United Kingdom: Yale University Press.

# Notes {data-icon="fas fa-pen"}

## column

### Data

The data are from the Annie E. Casey Kids Count website for Indiana. More specifically, the data were downloaded from the sections labeled "birth outcomes" and "early childhood".

### Technical

The heatmap and correlogram were generated via the `heatmaply` package in R. From the vignette, a "heatmap is a popular graphical method for visualizing high-dimensional data, in which a table of numbers are encoded as a grid of colored cells. The rows and columns of the matrix are ordered to highlight patterns and are often accompanied by dendrograms. Heatmaps are used in many fields for visualizing observations, correlations, missing values patterns, and more."

## column

### Resources

[Center for High Impact Philanthropy](https://www.impact.upenn.edu/early-childhood-toolkit/what-is-early-childhood/)

[Heckman: The Economics of Human Potential](https://heckmanequation.org)

[March of Dimes](https://www.marchofdimes.org)


### Acknowledgements

Thanks, attribution and acknowledgement are given to the following people and organizations:

[Annie E. Casey Foundation](https://www.aecf.org)

[Indiana Youth Institute](https://www.iyi.org)






