---
title: "Indiana Early Childhood"
output: 
  flexdashboard::flex_dashboard:
    theme: cerulean
    orientation: columns
    vertical_layout: fill
    source_code: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
library(magrittr)
library(dplyr)
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()
```

```{r load-data}
input <- "https://dl.dropbox.com/s/v8uef97q73zwq1j/2021-06-25-maternal-infant-health.csv?dl=0"
df <- data.table::fread(input = input)
# prepare data
rownames(df) <- df$location
df.1 <- df %>% select(-location)
```

# Maternal Health {data-icon="fa-table"}

## Column {data-width=500}

### Birth Outcomes


```{r heatmap}
load("./heatmap.Rdata")
m
```

## Column {data-width=500}

### Top 20 Indiana Counties by Live Births

```{r table}
library(DT)
row.names(df) <- NULL
DT::datatable(df, 
              extensions = 'FixedColumns',
              class = 'compact stripe',
              rownames = F,
  options = list(
    pageLength = 20,
    dom = 't',
    scrollX = TRUE,
    fixedColumns = list(leftColumns = 1)
  )) %>% 
  formatPercentage(columns = c(2:13), digits = 1)
```
### Infant Mortality {data-height=100}

Indiana reported 525 infant deaths in 2019.  According to the CDC [website](https://www.cdc.gov/reproductivehealth/maternalinfanthealth/infantmortality.htm), Indiana's infant mortality rate was 6.53 deaths per 1,000 live births, ranking Indiana 14th highest in the country by state. Infant mortality is the death of a child prior to his or her first birthday.

# Pre School

# Notes

Hello World!
